\begin{center}
\Large{\textbf{ABSTRACT}}
\end{center}
Scouting is an educational movement for young people with the help of adults. This movement is a large fraternity with more than 40 million members in 216 countries. Since 1907, when Baden-Powell founded Scouting, the membership and membership of the groups has increased with a large number of youth and adults spread across diverse groups around the world. The scout movement has a unique structure, where it has a hierarchy to be followed and, in this way, maintain a solid base created by the founder, so that this large mass of associates can conduct themselves with greater quality. Today we have many books, booklets and manuals that are used from the young person himself, in order to learn and improve educational techniques for personal growth, or even books used by adults who aim at personal development as a boss, seeking more and more for better knowledge to lead young people around them . As mentioned, scouting is rich in a vast library with books and materials for all tastes, but for those who prefer the technological use in União dos Scouts of Brazil, which is a national association, needed a system called Paxto and two applications that are the Young MAPPa and Adult MAPPa. These tools are used by all groups and have generic characteristics that the groups use to monitor the progression of young people, make available a collection of materials, attend to the activities of young people, among other options. Despite being programs of excellent quality, they are programs with a base of generic characteristics. Heads of the Local Scout Unit (UEL) of Lieutenant Laurentino, seek improvements for the activities and monitoring of the Scouts nowadays, considering the small number of adults available for daily activities. All, especially this need, was thought to develop a system capable of satisfying as an internal need of the group, and in this specific system for UEL, tools were thought to speed up and speed up the preparation of activities automatically, as well as the implementation of a cash system that is easy to be manipulated by the user, among other features of great importance for the youth and adults of the group.

\vspace{7cm}
\textbf{Keywords:}\hspace*{0.2cm}Browsea, inventory management, software for supermarkets.
